### 2018-05-08 README.Rmd
update readmes

# estimate the covariate-adjusted marginal mean for A = 1 and A = 0
# here, we do not properly estimate the propensity score
fit1 <- drtmle(W = W, A = A, Y = Y, # input data
               a_0 = c(0, 1), # return estimates for A = 0 and A = 1
               SL_Q = "SL.npreg", # use kernel regression for E(Y | A = a, W)
               glm_g = "W1 + W2", # use misspecified main terms glm for E(A | W)
               SL_Qr = "SL.npreg", # use kernel regression to guard against
                                   # misspecification of outcome regression
               SL_gr = "SL.npreg" # use kernel regression to guard against
                                  # misspecification of propensity score
              )
# print the output
fit1

@@

>>>>

# estimate the covariate-adjusted marginal mean for A = 1 and A = 0
# here, we do not properly estimate the propensity score
fit1 <- drtmle(W = W, A = A, Y = Y, # input data
               a_0 = c(0, 1), # return estimates for A = 0 and A = 1
               SL_Q = "SL.npreg", # use kernel regression for E(Y | A = a, W)
               glm_g = "W1 + W2", # use misspecified main terms glm for E(A | W)
               SL_Qr = "SL.npreg", # use kernel regression to guard against
                                   # misspecification of outcome regression
               SL_gr = "SL.npreg", # use kernel regression to guard against
                                  # misspecification of propensity score
               returnModels = TRUE # for visualizing fits later
              )
# print the output
fit1

@@

This method requires estimation of additional univariate regressions to ensure doubly robust confidence intervals and hypothesis tests. The method for estimation are input via `SL.Qr` and `SL.gr` or `glm.Qr` and `glm.gr` if parametric models are desired). These additional fits can be visualized by the `plot` method for `drtmle`. 
```r
layout(t(1:3))
plot(fit1, ask = FALSE)
```
